\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-12 chapters/5_experiments_intro.tex
Comments from Fred; move prop to appendix

\section{Experiments}\label{sec:neuro_segm_exp}
\subsection{Signed graph clustering problems}
We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs. The size of the graphs ranges from a few hundred to hundreds of millions of edges and the graphs have very different structures, so that the algorithms are tested in very different scenarios.

\textbf{Synthetic SSBM graphs} -- We first consider synthetic graphs generated by a signed stochastic block model (SSBM). We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma=0.1$. To model noise, the sign of the edge weights is flipped independently with probability $\eta$.

@@

\subsection{Comparison results and discussion}
% Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.

\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:all_multicut_energies}, in Appendix.}. Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here. By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances. Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}). 
% To better understand these empirical results, we now make the following important observation.
% This can also be observed in our experiments on synthetic graphs (Fig. ? and ?), where the clustering with minimum multicut energy become very different from the ground truth clustering when the flip noise parameter $\eta$ is increased.

@@

\textbf{GASP on synthetic SSBM graphs}  -- 
% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, almost as good as the spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}). Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results. 
In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities. From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (see dendrograms in Fig.~\ref{fig:dendrograms}). Average linkage method HC-Avg instead performs much worse on these graphs because it grows small equally-sized clusters and makes several wrong merge-decisions at the beginning. 
% This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here. 
Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise. In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see \TODO{Appendix}), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.

\textbf{Complete and Single Linkage} -- We use these two linkage methods as baselines to highlight the difficulty of the studied graph clustering problems listed in Table~\ref{tab:datasets_and_energies}. Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performances: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters. HC-Complete and HCC-Complete returned instead a lot of over-segmented clusters. 
% These algorithms are excluded from our next comparison experiments.

@@

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar}, where every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (\emph{HC-Avg}, \emph{HCC-Avg}) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (\emph{GAEC}, \emph{HCC-Sum}) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods performs poorly on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}). It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how \emph{MWS} can achieve competitive performances with considerably lower runtimes.

\begin{figure}
\centering
% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$, $p=0.05$, $\eta=0.1$, and $k=2$ communities of equal size).  Red and blue colors represent the true community of each initial node. At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number). \label{fig:dendrograms}}
\end{figure}

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut formulation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information. 
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
\caption{Failure cases of three versions of \algname{} on challenging parts of the CREMI dataset. \emph{Wrongly} segmented regions are highlighted in different warm colors. Red arrows point to wrongly split regions; yellow ones to merge errors. HC-Avg returned the best segmentation. Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  
\label{fig:failure_cases}}
\end{figure}

>>>>

\section{Experiments}\label{sec:neuro_segm_exp}
\subsection{Signed graph clustering problems}
We evaluate the agglomerative clustering algorithms included in our framework on a large collection of both synthetic and real-world graphs with very different structures. The size of the graphs ranges from a few hundred to hundreds of millions of edges.

\textbf{Synthetic SSBM graphs} -- We first consider synthetic graphs generated by a signed stochastic block model (SSBM). We use an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N$ vertices and edge probability $p$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k$ \emph{ground-truth} clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) have Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $\sigma=0.1$. To model noise, the sign of the edge weights is flipped independently with probability $\eta$.

@@

\subsection{Comparison results and discussion}\label{sec:experiments_discussion}
% Before to evaluate the clustering algorithms on real-world graphs, we compare them on two types of synthetically generated graphs and highlight some of their fundamental properties.

\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:all_multicut_energies}, in Appendix.}. Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here. By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances. Despite this, on graphs where a GT clustering is known, GAEC does not achieve the lowest ARAND errors (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}). 
% To better understand these empirical results, we now make the following important observation.
% This can also be observed in our experiments on synthetic graphs (Fig. ? and ?), where the clustering with minimum multicut energy become very different from the ground truth clustering when the flip noise parameter $\eta$ is increased.

@@

\textbf{GASP on synthetic SSBM graphs}  -- 
% can be connected to any  that, depending on the edge-probability parameter $p$, are also \emph{dense}. 
\algname{} algorithms using cannotLinkConstraints are not expected to perform well on these graphs, because of the type of employed flip noise, so we focus our comparison only on the GAEC, HC-Avg and MWS algorithms (using Sum, Average, and AbsMax linkage methods, respectively).
Empirically, we observe that GAEC is the agglomerative algorithm performing best on SSBM graphs, on par with spectral method SPONGE$_{sym}$ (see Fig.~\ref{fig:SSBM_scores}). Given the simple properties of SSBM graphs, we will now give a specific explanation of these empirical results. 
In SSBM graphs, the number of edges $E_{ij}\equiv(S_i\times S_j)\cap E$ connecting two clusters $S_i,S_j$ is  proportional to the product $|S_i|\cdot|S_j|$ of cluster sizes. 
With Sum or Avg linkage methods, due to the law of large numbers, the flipping noise is ``averaged out'' as soon as the set $E_{ij}$ becomes larger and clusters grow in size.
On the other hand, when clusters are small, it is more likely that several of the edges in $E_{ij}$ are flipped and the algorithm makes a mistake by merging two clusters belonging to different ground truth communities. From this observation, it follows that the \emph{flooding strategy} of the sum-linkage algorithm GAEC is a very good strategy on these types of graphs, because clusters are immediately grown in size (see dendrograms in Fig.~\ref{fig:dendrograms}). Average linkage method HC-Avg instead performs much worse on these graphs because it grows small equally-sized clusters and makes several wrong merge-decisions at the beginning. 
% This observation also explains the empirical results of \cite{chehreghani2020hierarchical}, which involved graph instances with very similar structure to the ones considered here. 
Lastly, the MWS algorithm is not expected to perform well on these graphs because of the high sensitivity of the AbsMax linkage to flipping noise. In Propositions \ref{prop:MWS_SSBM_1} and \ref{prop:MWS_SSBM_2} (see \TODO{Appendix}), we prove that on SSBM graphs the merging steps of the MWS algorithm are given by a sequence of ``coin flip'' decisions with a probability proportional to the noise parameter $\eta$, independently on the cluster sizes.

\textbf{Complete and Single Linkage} -- We use these two linkage methods as baselines to highlight the difficulty of the studied graph clustering problems listed in Table~\ref{tab:datasets_and_energies}. Scores in Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show their poor performances: Single linkage hierarchical clustering (HC-Single), which here is equivalent to thresholding the edge weights at $w_e=0$ and computing connected components in the graph, often returned few big under-segmented clusters. HC-Complete returned instead a lot of over-segmented clusters. 
% These algorithms are excluded from our next comparison experiments.

@@

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar}, where every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods performs poorly on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS). It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve competitive performances with considerably lower runtimes.

\begin{figure}
\centering
% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
\caption{Dendrograms built by three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).  Red and blue colors represent the ground-truth community of each node (two communities of equal size). At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{} (y-axis shows the iteration number). \label{fig:dendrograms}}
\end{figure}

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information. 
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
\caption{Failure cases of three versions of \algname{} (GAEC, MWS, and HC-Avg) applied to neuron segmentation. \emph{Wrongly} segmented regions are highlighted in different warm colors. Red arrows point to wrongly split regions; yellow arrows point to merge errors. HC-Avg returned the best segmentation. Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  
\label{fig:failure_cases}}
\end{figure}

### 2021-03-12 chapters/supplementary.tex
Comments from Fred; move prop to appendix

\firstUltraMetricProperty*
\begin{proof}
% Let us first analyze assumption \ref{eq:UM_assumption}. From $(\Rightarrow)$, we have that:
% \begin{equation}\label{eq:assumption_side_1}
% h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
% \end{equation}
% In words, if the algorithm first merges node $v$ together with node $u$ and later on merges node $t$ with node $u$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be stronger than $\interact{}_{T}(u,t)$. On the other hand, the $(\Leftarrow)$ side of Eq.~\ref{eq:UM_assumption} can be rewritten as:
% \begin{equation}\label{eq:assumption_side_2}
% h_T(u \vee v) \geq h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \leq \interact{}_{T}(u,t).
% \end{equation}
% % which in words means: if node $t$ was merged with $u$ at the same or at an earlier iteration  together with node $u$ and later on merges node $t$ with node $u$, then the interaction $\interact{}_{T}(u,v)$

@@

Thanks to Lemma \ref{lemma:absMax_and_complete_property}, we have that condition 2 always holds for algorithms based on AbsMax and Complete linkage, proving that the Mutex Watershed and HC-Complete algorithms define an ultra-metric (whether or not cannot-link-constraints are enforced). On the other hand, condition 2 does not hold for other variations of \algname{} involving cannot-link-constraints (HCC-Sum, HCC-Avg, and HCC-Single), which do not define then an ultrametric.

>>>>

\begin{restatable}{prop}{firstUltraMetricProperty}
\label{prop:ultraMetric1}
Consider a graph $\mathcal{G}(V,E,w_e)$, a linkage criterion $\interact{}$, and an agglomerative algorithm returning a binary rooted tree $T$ with height $h_T$. Then, $(V, d_{T})$ defined in Eq.~\ref{eq:UM_def} is an ultrametric if and only if the following is true:
 % iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than the interaction of any other $(u\vee v)$-descendant node and higher than the interaction of any other $(u\vee v)$-ancestor node in the tree $T$. In formulae, this is equivalent to saying that, $\forall u,v,t \in V$:
\begin{equation}\label{eq:UM_assumption}
 h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \geq \interact{}_{T}(u,t).
 % h_T(u \vee v) < h_T(u \vee t) \Leftrightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
\end{equation}
In words, condition \ref{eq:UM_assumption} means: if the algorithm merges nodes $u,v$ before to merge nodes $u,t$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be higher or equal than $\interact{}_{T}(u,t)$.
% In words, $(V, d_{T})$ is an ultrametric iff the interaction $\interact{}_{T}(u, v)$ associated to the least common ancestor ${(u\vee v)\in T}$ is both lower than any other $(u\vee v)$-descendant node and higher than any other $(u\vee v)$-ancestor node in the tree $T$.
\end{restatable}
\begin{proof}
% Let us first analyze assumption \ref{eq:UM_assumption}. From $(\Rightarrow)$, we have that:
% \begin{equation}\label{eq:assumption_side_1}
% h_T(u \vee v) < h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) > \interact{}_{T}(u,t). 
% \end{equation}
% In words, if the algorithm first merges node $v$ together with node $u$ and later on merges node $t$ with node $u$, then the signed interaction $\interact{}_{T}(u,v)$ between $u$ and $v$ has to be stronger than $\interact{}_{T}(u,t)$. On the other hand, the $(\Leftarrow)$ side of Eq.~\ref{eq:UM_assumption} can be rewritten as:
% \begin{equation}\label{eq:assumption_side_2}
% h_T(u \vee v) \geq h_T(u \vee t) \Rightarrow \interact{}_{T}(u,v) \leq \interact{}_{T}(u,t).
% \end{equation}
% % which in words means: if node $t$ was merged with $u$ at the same or at an earlier iteration  together with node $u$ and later on merges node $t$ with node $u$, then the interaction $\interact{}_{T}(u,v)$

@@

Thanks to Lemma \ref{lemma:absMax_and_complete_property}, we have that condition 2 always holds for algorithms based on AbsMax and Complete linkage, proving that the Mutex Watershed and HC-Complete algorithms define an ultra-metric (whether or not cannot-link-constraints are enforced). On the other hand, condition 2 does not hold for other variations of \algname{} involving cannot-link-constraints (HCC-Sum, HCC-Avg, and HCC-Single), which do not then define an ultrametric.
